---
title: "Starigtlining effects"
author: "Xilin Chen"
date: "1/6/2021"
output: pdf_document
---

Explore straightlining effects in the end-year evaluations in PGY5. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  dev = 'png',
  fig.align = 'center',
  cache = F
  # out.width = '100%',
  # fig.asp = .5,
)    

library(dplyr)
library(stringr)
library(ggplot2)
library(kableExtra)

```


```{r load data}
# filtered cohort for primary cases (for analysis)
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_pc_primary.rdata")
# original milestone
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_final_year.rdata")
```


```{r data prep}
milestone_24 = milestone_medicare_pc_primary %>% 
  filter(month<=24)

# persons included in analysis
person <- milestone_24 %>%   
  distinct(id_physician_npi, PersonID)

# create flag to show if the residents were included in analyses
milestone_end_year <- milestone_final_year %>% 
  filter(str_detect(eval_peroid, "End")) %>% 
  mutate(included_in_analysis = ifelse(PersonID %in% person$PersonID, 1, 0))
```

## straight lining for the analysis cohort

n_rep: number of repeated ratings

12.68% of trainees received all same ratings at the PGY5 end year evals; 4.26% of traines received same 15/16 ratings.
```{r straigtline_assess}
straightine_person = milestone_end_year %>% 
  filter(included_in_analysis ==1 ) %>% 
  select(PersonID, IntResponseValue) %>% 
  add_count(PersonID, IntResponseValue, name = "n_rep") %>% 
  distinct()

straightine_person %>% 
  tidyext::cat_by(n_rep) %>% 
  filter(n_rep<17, n_rep>10) %>% 
  kable(digits = 2) %>%
  kable_styling(full_width = F)
```


Among the 122 straightlined trainees,  110% of them has received all 9 ratings.

```{r}
straightine_person %>% 
  filter(n_rep == 16) %>% 
  count(IntResponseValue) %>% 
  kable(digits = 2) %>%
  kable_styling(full_width = F)
```


## straight lining for the whole GS group

```{r}
straightine_person_gs = milestone_end_year %>% 
  select(PersonID, IntResponseValue) %>% 
  add_count(PersonID, IntResponseValue, name = "n_rep") %>% 
  distinct()

straightine_person_gs %>% 
  tidyext::cat_by(n_rep) %>% 
  filter(n_rep<17, n_rep>10) %>% 
  kable(digits = 2) %>%
  kable_styling(full_width = F)
```

```{r}
straightine_person_gs %>% 
  filter(n_rep == 16) %>% 
  count(IntResponseValue) %>% 
  kable(digits = 2) %>%
  kable_styling(full_width = F)
```


## straight lining for the whole GS group for **Mid-year** PGY5

```{r}
straightine_person_gs_med = milestone_final_year %>% 
  filter(str_detect(eval_peroid, "Mid")) %>% 
  mutate(included_in_analysis = ifelse(PersonID %in% person$PersonID, 1, 0)) %>% 
  select(PersonID, IntResponseValue) %>% 
  add_count(PersonID, IntResponseValue, name = "n_rep") %>% 
  distinct() 

straightine_person_gs_med %>% 
  tidyext::cat_by(n_rep) %>% 
  filter(n_rep<17, n_rep>10) %>% 
  kable(digits = 2) %>%
  kable_styling(full_width = F)


straightine_person_gs_med %>% 
  filter(n_rep == 16) %>% 
  count(IntResponseValue) %>% 
  kable(digits = 2) %>%
  kable_styling(full_width = F)
  
```


