---
title: "Milestone Evals"
author: "Xilin Chen"
date: "2/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  dev = 'png',
  fig.align = 'center',
  cache = F
  # out.width = '100%',
  # fig.asp = .5,
)    

library(tidyverse)
library(kableExtra)
library(lubridate)
library(tidyext)


kable_df <- function(..., digits=2) {
  kable(...,digits = digits) %>% 
    kable_styling(full_width = F, latex_options = "hold_position")
}
```

This document explores the milestone data for the last year evaluation

```{r load_data}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_final_year.rdata")
load("data/person_in_medicare_and_milestone.rdata")

milestone_in_medicare = milestone_final_year %>% 
  mutate(IntResponseValue = ifelse(IntResponseValue == 0, NA, IntResponseValue)) %>% 
  filter(grepl("Year-End",eval_peroid),
         PersonID %in% person_values$PersonID)
```


# Descriptive of Milestone

Evaluations are from 2015 to 2018, Mid-year and Year-end evals within each year. The number of graduates in milestone evals and also in Medicare are `r n_distinct(milestone_in_medicare$PersonID)`

```{r evals}
milestone_in_medicare %>% 
  cat_by(eval_peroid) %>% 
  kable_df()
```

How many residents have <7 evals

```{r low_eval}
milestone_in_medicare %>% 
  filter(IntResponseValue<7) %>% 
  summarise(n_trainees_less_7 = length(unique(PersonID)),
            n_tot_trainees = length(unique(milestone_in_medicare$PersonID))) %>% 
  kable_df()

milestone_in_medicare %>% 
  filter(!is.na(IntResponseValue)) %>% 
  count(IntResponseValue, ReportCategory) %>% 
  ggplot(aes(x = IntResponseValue, y = ReportCategory)) +
  geom_point(aes(size = n), color = "gray50")


milestone_in_medicare %>% 
  filter(QuestionKey %in% c("comp1_PC_Q3", "comp2_MK_Q2", "comp6_ICS_Q3")) %>% 
  ggplot(aes(x = IntResponseValue)) +
  stat_count(color = "gray50") +
  ggtitle("Operative Rating (PC3, MK2, ICS3)")

milestone_in_medicare %>% 
  filter(ReportCategory == "Professionalism") %>% 
  ggplot(aes(x = IntResponseValue)) +
  stat_count(color = "gray50") +
  ggtitle("Professionalism (Prof1, Prof 2, Prof3)")

```





