---
title: "Interaction"
author: "Xilin Chen"
date: "12/14/2020"
output: pdf_document
---

Explore interactions between milestone ratings and whether had assistant surgeon in the case.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  dev = 'png',
  fig.align = 'center',
  cache = F
  # out.width = '100%',
  # fig.asp = .5,
)    

library(tidyverse)
library(glmmTMB)
library(mixedup)
library(kableExtra)
library(emmeans)

```

```{r data_prep, cache=T}
# explore interactions
# load 24 months ------
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/model/models_month24_pc_interaction_no_case_vol.rdata")

# 1. OR ----------------------------------------------------------------------
# ratings by category
model_tables = map_df(results, extract_fixed_effects, .id = "outcome")

# process
model_tables = model_tables %>%
  mutate(
    OR = exp(value),
    OR_lower = exp(lower_2.5),
    OR_upper = exp(upper_97.5)
  ) %>%
  mutate(outcome = str_remove_all(outcome, pattern = c("Par_"))) %>%
  select(outcome, term, value, OR, contains("OR"), p_value) 

```

## 1. Summary table for all ratings and had_assist_surgeon interactions model results

- interaction term for ratings and assistant surgeon

```{r}
# interaction ----
all_inter_terms = model_tables  %>%
  filter(str_detect(term, ":")) %>% 
  rename(coef = value) %>% 
  mutate_if(is.numeric,~round(.,2))  %>% 
  mutate(
    outcome = case_when(
      str_detect(outcome, "severe_cmp") ~ "severe_cmp",
      str_detect(outcome, "any_cmp") ~ "any_cmp",
      str_detect(outcome, "readmit") ~ "readmit",
      str_detect(outcome, "death") ~ "death",
      TRUE ~ as.character(term)
    )
  )

all_inter_terms %>% 
  kable(digits = 2) %>%
  kable_styling(full_width = F) %>% 
  collapse_rows(columns = 1, valign = "top") 
```

## 2. Example model: overall rating binary vs. severe complication model

32 models were used for the table summary above. We explore one example from all the models above.


### Model summary

- binary milestone ratings for severe complications

```{r}
 # example model interpretation
 # overall mean ≥8
 sever_cmp_overall_bin8 = results$Par_severe_cmp_mean_ge_8

 # coef table
 extract_fixed_effects(sever_cmp_overall_bin8) %>%
     kable(digits = 2) %>%
     kable_styling(full_width = F)

 extract_vc(sever_cmp_overall_bin8) %>%
     kable(digits = 2) %>%
     kable_styling(full_width = F)
```

### interaction interpretations

1. table of effects by category

```{r}
em_model <- emmeans(sever_cmp_overall_bin8, "mean_ge_8", by = "had_assist_surg", type = "response")

# contrast of odds ratio
em_model_pw <- emmeans(sever_cmp_overall_bin8, pairwise ~ mean_ge_8*had_assist_surg, type = "response")

em_model_pw
```

- when a sugeon had <8 overall rating and didn't have assistant surgeon in the case, the probability of the patient having severe complication is 16.57%, fixing all covariates at average level.


2. plot

predicted prob by had vs didn't have assistant surgeon in the case.

```{r}
#p = emmip(sever_cmp_overall_bin8, as.factor(mean_ge_8) ~ as.factor(had_assist_surg),CIs=TRUE, type = "response")
p = emmip(results$Par_any_cmp_mean_ge_8, as.factor(mean_ge_8) ~ as.factor(had_assist_surg),CIs=TRUE, type = "response")
# p

ggplot(data = p$data %>%
         mutate(had_assist_surg = factor(
           had_assist_surg,
           labels = c("No assistant surgeon", "Had assistant surgeon")
         )),
       aes(
         x = factor(mean_ge_8, labels = c("Not Yet Proficient", "Proficient")),
         y = yvar,
         group = factor(had_assist_surg)
       ))+
  geom_col(
  aes(
    fill = factor(had_assist_surg),
  ),
  position = position_dodge(width = 0.55), width = 0.4
) +
  geom_errorbar(aes(ymin = LCL, ymax = UCL),
                alpha = 0.7, position = position_dodge(width = 0.55),
                width = .2, show.legend = FALSE) +
  scale_color_manual(values = c("gray40", "gray85"), aesthetics = c("fill")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(y = "Probabilities of having any complications",
       caption = "The interaction effect of overall Milestone ratings and presence of assistant surgeons (p value = 0.28)",
       color = "") +
  visibly::theme_trueMinimal(center_axis_labels = T) +
  theme(axis.line.x = element_line(colour="black"),
        axis.line.y = element_line(colour="black"),
        axis.title.x=element_blank(),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(size = 10),
        # axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(angle = 90, vjust = 0.5, size = 13),
        axis.ticks.y=element_blank(),
        strip.text = element_text(size = 13),
        legend.position="bottom",
        legend.key.size = unit(0.5, "cm"),
        legend.title = element_blank(),
        plot.caption = element_text(size = 10)) 

ggsave("images/interaction_assist_surg_overall_rating_any_cmp.png")
# ggsave("images/interaction_assist_surg_overall_rating_no_error_bar.png")
  
```

