---
title: "Distribution for continuous milestone ratings"
author: "Xilin Chen"
date: "12/14/2020"
output: 
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  dev = 'png',
  fig.align = 'center',
  cache = F
  # out.width = '100%',
  # fig.asp = .5,
)    

library(tidyverse)
library(kableExtra)
library(lubridate)
library(tidyext)
```

```{r}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_pc_primary.rdata")

# original milestone
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_final_year.rdata")


# filter only 24 after graduation cases
main_data = milestone_medicare_pc_primary %>% 
  filter(month<=24)

person_milestone_rating = main_data %>% 
  distinct(PersonID, IntResponseValue_mean, operative_rating_mean, leadership_rating_mean, prof_rating_mean) %>% 
  rename(overall_mean = IntResponseValue_mean)
```

## summary

Partial Colectomy medicare cases by milestone graduates within 24 of graduation.


```{r}
main_data %>% 
  summarise(n_case = n(),
            n_surgeon = length(unique(id_physician_npi)),
            n_hosp = length(unique(facility_prvnumgrp)),
            n_patient = length(unique(member_id))) %>% 
  kable() %>% 
  kable_styling(full_width = F)
```



content

- Explore cutoffs for % Trainees Overall Mean Milestone ratings  (0-7, 8, 9 vs. 0-8, 9)
- Histogram for continuous milestone ratings
- Critical deficiency group (using all pgy 5 milestone group)
  - how many residents have 1,2,3, end-year evaluation at PGY5 (n)
  - check 1,2,3 for outliers
  - meaning of 0 rating (NA vs. critical deficiency)


## Binary milestone rating tables

```{r}
binay_summary <- function(data, rating_var, score) {
  bin_var = paste0(rating_var, "_bin", score)
  
  data %>%
    mutate(!!bin_var := ifelse(!!rlang::sym(rating_var) >= score,
                               1, 0)) %>% 
    group_by(!!rlang::sym(bin_var)) %>% 
    summarise(n_case = n(),
            n_surgeon = length(unique(id_physician_npi)),
            n_patient = length(unique(member_id)))
    # kable() %>% 
    # kable_styling(full_width = F)
}

var_list = c("IntResponseValue_mean", "operative_rating_mean", "leadership_rating_mean", "prof_rating_mean")
```

### Binary by rating 8

```{r}
bin8 = map(var_list, ~binay_summary(data = main_data,
              rating_var = .x,
              score = 8) )

names(bin8) = var_list
bin8
```


### Binary by rating 9

```{r}
bin9 = map(var_list, ~binay_summary(data = main_data,
              rating_var = .x,
              score = 9))

names(bin9) = var_list
bin9

```

In the subcategory rating groups, half of the trainees had perfect 9 rating.

\break

## Plot: Distribution of 4 mean milestone ratings


```{r}
histogram_rating <- function(data, rating_var) {
  cnt = data %>%
    count(!!rlang::sym(rating_var))

  ggplot(data = cnt,
         aes(x = !!rlang::sym(rating_var), y = n,
             label = n)) +
    geom_col() +
    geom_text(check_overlap = TRUE,
              vjust = -0.5,
              angle = 45) +
    labs(y = "number of trainees") +
    theme_bw()
}

# histogram_rating(data = person_milestone_rating,
#                                    rating_var = "overall_mean")

rating_vars = c("overall_mean", "operative_rating_mean", "leadership_rating_mean", "prof_rating_mean")

histo_plots = map(rating_vars, ~histogram_rating(data = person_milestone_rating,
                                   rating_var = .x))

names(histo_plots) = rating_vars

histo_plots 
```


## Critical deficiency group

Cohort

- original milestone ratings (without linking to medicare)
- end-year evals at PGY5


```{r}
year_end_evals = milestone_final_year %>% 
  filter(str_detect(eval_peroid, "Year-End"))

year_end_evals %>% 
  group_by(eval_peroid) %>% 
  summarise(n_evals = n(),
            n_person = length(unique(PersonID))) %>% 
  kable() %>% 
  kable_styling(full_width = F)
```

### Overall ratings distribution

```{r}
histogram_rating(data = year_end_evals,
                 rating_var = "IntResponseValue") +
  labs(caption = "1 person with 16 evals")
```

```{r}
mean_cnt = year_end_evals %>%
  mutate(IntResponseValue = as.integer(IntResponseValue)) %>%
  group_by(PersonID) %>%
  summarise(mean_eval = mean(IntResponseValue, na.rm = T))

histogram_rating(data = mean_cnt,
                 rating_var = "mean_eval") +
  scale_x_continuous(breaks = c(0, 1,2, 3,4,5, 6, 7,8,9)) +
  labs(caption = "mean over 16 eval ratings per person")
```


There are very few outliers.

In our analysis, we treated rating 0 as NA based on the milestone rating definition. There are very few cases having 0 ratings.



