---
title: "QA the mortality rates in milestone medicare outcomes"
author: "Xilin Chen"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  fig.align = 'center',
  cache = F
)

kable_df <- function(..., digits = 3) {
  kable(
    ...,
    format = 'latex',
    booktabs = TRUE,
    linesep = '',  # removes spacing every 5 lines
    digits = digits
  ) %>%
    kable_styling(full_width = FALSE)
}

source("~/Documents/Repo/Medicare_analytics_ECS/code/functions/prep_data_for_model.R")
source("~/Documents/Repo/Milestone_Medicare_Outcomes/code/functions/my_summary.R")

library(tidyverse)
library(kableExtra)
```

updated in December 2020.

- only keep partial colectomy procedure
- death rate stratify by age and case emergecy status
- QA 10 patients death

## 1. Compare descriptive stats among different cohorts

### Cohort Description

-   Milestone Medicare

    -   2015-2017 medicare cases by milestone graduates from 2015-2017 within 24 months after graduation
    -   Partial Colectomy

-   ECV

    -   2006 - 2016 medicare cases by general surgery surgeons within 35 years of practice
    -   Partial Colectomy

-   Medicare 2007-2017

    -   Medicare 5 procedures from 2007 to 2017 standardized using R
    -   Partial Colectomy

```{r load_data, cache=TRUE}
# milestone -------
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_pc_primary.rdata")

# ECV-------
ecv =  qs::qread('/Volumes/George_Surgeon_Projects/early_career_variability/medicare_ecv_model_ready.qs') 

ecv = ecv %>%
  mutate(
    flg_cmp_po_severe_not_poa = ifelse(facility_clm_yr < 2010, NA, flg_cmp_po_severe_poa),
    flg_cmp_po_any = ifelse(facility_clm_yr < 2010, NA, flg_cmp_po_any)
  ) 


# medicare 07-17------
medicare_07_17 = data.table::fread("/Volumes/George_Surgeon_Projects/standardized_medicare_data_using_R/analysis_ready_data/analytic_selected_vars.csv")
# keep partial colectomy
medicare_07_17_pc = medicare_07_17[e_proc_grp_lbl == "Partial Colectomy"]

```

```{r data_process}
# milestone 24 months------
milestone_medicare_pc = milestone_medicare_pc_primary %>% 
  filter(!is.na(IntResponseValue_mean),
         month <= 24)

milestone_medicare_pc = milestone_medicare_pc %>%  # for later to get mean rate
  mutate(flg_cmp_po_any_not_poa = as.numeric(flg_cmp_po_any_not_poa),
         flg_cmp_po_severe_not_poa = as.numeric(flg_cmp_po_severe_not_poa)) 

# medicare 2007-2017 ------
medicare_07_17_pc = medicare_07_17_pc %>%
  mutate(
    flg_cmp_po_any_not_poa = as.numeric(flg_cmp_po_any_not_poa),
    flg_cmp_po_severe_not_poa = as.numeric(flg_cmp_po_severe_not_poa)
  )

#ECV -------
ecv = ecv %>% 
      prep_data_for_model(
        cohort = c(
          "id_physician_npi != ''",
          '!is.na(val_yr_practice)',
          # 'surgeon_N_cases >= 10',
          'val_yr_practice >= 0 & val_yr_practice <= 35',
          "proc_Partial_Colectomy == 1"
        ),
        one_hot = NULL,
        standardize = NULL
      ) 
```

**Descriptive Stats**

```{r cmp_tbl}
milestone_tbl1 = milestone_medicare_pc %>%
  my_summary() %>% 
  mutate(cohort = "milestone") %>% 
  select(cohort, everything())

# medicare 2007-2017
medicare_tbl1 = medicare_07_17_pc %>%
  my_summary() %>% 
  mutate(cohort = "medicare_06_17") %>% 
  select(cohort, everything())


ecv_tbl1 = ecv %>%
  my_summary() %>% 
  mutate(cohort = "ecv") %>% 
  select(cohort, everything()) 

```

compare descriptive stats among different datasets

```{r combine}
df = rbind(milestone_tbl1 ,ecv_tbl1, medicare_tbl1)

as_tibble(cbind(` ` = names(df), t(df))) %>%
  rename(milestone = V2, ecv = V3, medicare07_17 = V4) %>%
  slice(-1) %>%
  kable() %>%
  kable_styling(full_width = F)
```

\pagebreak

## 2. Stratify death rate by patient age

```{r}
# milestone -----
milestone_medicare_pc = milestone_medicare_pc %>%
  # one pt can have multiple ages due to claim year, so don't distinct patient
  mutate(
    age_grp = case_when(
      age_at_admit <= 80 ~ "65-80",
      age_at_admit > 80 &
        age_at_admit <= 99 ~ "81-99"
      # age_at_admit > 99 ~ "99+" # no >99 group
    )
  )

by_age_milestone = milestone_medicare_pc %>% 
  group_by(age_grp) %>% 
  my_summary() %>% 
  mutate(cohort = "milestone") %>% 
  select(cohort, everything())

# ecv -------
ecv = ecv %>%
  mutate(
    age_grp = case_when(
      age_at_admit <= 80 ~ "65-80",
      age_at_admit > 80 &
        age_at_admit <= 99 ~ "81-99"
      # age_at_admit > 99 ~ "99+" # no >99 group
    )
  )

by_age_ecv = ecv %>% 
  group_by(age_grp) %>% 
  my_summary() %>% 
  mutate(cohort = "ecv") %>% 
  select(cohort, everything())


# medicare -----
medicare_07_17_pc = medicare_07_17_pc %>%
  mutate(
    age_grp = case_when(
      age_at_admit <= 80 ~ "65-80",
      age_at_admit > 80 &
        age_at_admit <= 99 ~ "81-99"
      # age_at_admit > 99 ~ "99+" # no >99 group
    )
  )

by_age_medicare = medicare_07_17_pc %>% 
  group_by(age_grp) %>% 
  my_summary() %>% 
  mutate(cohort = "medicare") %>% 
  select(cohort, everything())

# combine 3 datasets
age_df = rbind(by_age_milestone ,by_age_ecv, by_age_medicare)

as_tibble(age_df) %>%
  arrange(age_grp) %>% 
  rename(complication = POA_severe_cmp_rate) %>% 
  select(age_grp, cohort, death_rate, everything()) %>% 
  kable() %>%
  kable_styling(full_width = F)
```

81-99 age group had higher 30 day's mortality rates.


## 3. Stratify death rate by case emergency

```{r}
medicare_07_17_pc = medicare_07_17_pc %>% 
  mutate(flg_admit_emerg = case_when(e_admit_type %in% c("1_Emergency", "2_Urgent") ~ 1,
                                     e_admit_type %in% c("3_Elective") ~ 0)) 

data_list = list(milestone_medicare_pc, ecv, medicare_07_17_pc)
names(data_list) = c("milestone", "ecv", "medicare")

by_emerg_death_rate = imap_dfr(data_list, function(data, name) {
  data %>% 
  group_by(flg_admit_emerg) %>% 
  my_summary() %>% 
  mutate(cohort = name) %>% 
  select(cohort, everything())
})

by_emerg_death_rate %>% 
  arrange(flg_admit_emerg) %>% 
  rename(complication = POA_severe_cmp_rate) %>% 
  select(emergent = flg_admit_emerg, cohort, death_rate, everything()) %>% 
  kable() %>%
  kable_styling(full_width = F)

```

Emergent cases had higher 30 days mortality rates.

## 4. check 10 patients death manually

- step1: find 10 different cases that death =1
- step2: extract facility claim ID for the cases
- step3: find facility claim in original MedPAR using facility claim ID
- step4: find the status at discharge. [BENE_DSCHRG_STUS_CD](https://www.resdac.org/cms-data/variables/medpar-beneficiary-discharge-status-code)

```{r}
set.seed(123)
sample_10 = milestone_medicare_pc %>% 
  filter(flg_death_30d ==1, str_detect(dt_facclm_adm, "2015")) %>% 
  distinct(id, member_id, dt_facclm_adm) %>% sample_n(10)
# save(sample_10, file = "/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/sample_10.rdata")
# sample original Medpar 2015
medpar_sample = read_csv("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/sample10_medpar.csv")

medpar_sample %>% 
  select(BENE_ID, BENE_DSCHRG_STUS_CD) %>% 
  mutate(BENE_ID = hashed_id(BENE_ID, "somesalt1234")) %>% 
  mutate(discharge_loc = case_when(BENE_DSCHRG_STUS_CD == "A" ~ "Discharged alive",
                                   BENE_DSCHRG_STUS_CD == "B" ~ "Discharged dead",
                                   BENE_DSCHRG_STUS_CD == "C" ~ "Still a patient")) %>% 
  select(-BENE_DSCHRG_STUS_CD) %>% 
  kable() %>%
  kable_styling(full_width = F)

```

6 out of 9 patients were dead at hospital discharge.
