---
title: "General Surgery Definitions Carrier vs. NPPES"
author: "Xilin Chen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  fig.align = 'center',
  cache = F
)

library(tidyverse)
library(kableExtra)

kable_df <- function(..., digits=2) {
  kable(...,digits = digits, booktabs = T) %>% 
    kable_styling(full_width = F,
                  latex_options = c("striped", "hold_position"))
}

```

```{r data, cache=T}
load("data/milestone_person_us_no_fellow.rdata")
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/medicare_gs_by_abs.rdata")
# qa data
load("data/qa_surg.rdata")
load("data/qa_surg_gs_npi_no_gs_carrier.rdata")


milestone_medicare =  milestone_person_us_no_fellow %>% 
  left_join(medicare_gs, by = c("npi.linked" = "id_physician_npi"))
```

Compare the differences between using Carrier file and NPPES to define general surgery specialty surgeons. In Carrier file definition, GS was defined as surgeons that only had GS as their specialty for all medicare cases. In NPPES, GS was defined as surgeons who only listed GS as their primary specialty.


- The number of surgeons in Milestone before filter GS specialty is `r nrow(milestone_person_us_no_fellow)`.

Carrier vs NPPES definition

```{r comp}
milestone_person_us_no_fellow %>% 
  count(carrier_nppes_gs, npi_nppes_gs, name = "n surgeons") %>% 
  kable_df()
```

- Carrier GS, NPPES Not GS

Among the 119 surgeons who are defined as GS in carrier but not NPPES NPI file, before is ther specilty definition in NPPES file

```{r nppes_splty}
# nppes is not gs, carrier all gs procedures
npi_list = milestone_person_us_no_fellow %>%
  filter(carrier_nppes_gs =="gs" , npi_nppes_gs =="not gs") %>%
  pull(npi.linked) %>% 
  unique()

# nppes isgs, carrier not all gs procedures
npi_list2 = milestone_person_us_no_fellow %>%
  filter(carrier_nppes_gs =="not gs" , npi_nppes_gs =="gs") %>%
  pull(npi.linked)

# npi_taxonomy = data.table::fread(
#   "/Volumes/George_Surgeon_Projects/Other/NPPES_Data_Dissemination_January_2020/npi_taxonomy_individual.csv"
# )
# qa_surg = npi_taxonomy %>%
#   mutate(NPI = as.character(NPI)) %>%
#   filter(NPI %in% npi_list) %>%
#   janitor::clean_names()
# 
# save(qa_surg, file = "data/qa_surg.rdata")

# qa_surg_gs_npi_no_gs_carrier = npi_taxonomy %>%
#   mutate(NPI = as.character(NPI)) %>%
#   filter(NPI %in% npi_list2) %>%
#   janitor::clean_names()
# 
# save(qa_surg_gs_npi_no_gs_carrier, file = "data/qa_surg_gs_npi_no_gs_carrier.rdata")

qa_surg = qa_surg %>%
  mutate(degree = ifelse(str_detect(provider_credential_text, "M.D|MD"), "with MD", NA),
         degree = ifelse(str_detect(provider_credential_text, "D.O|DO"), "with DO", degree))

qa_surg %>% 
  distinct(npi, degree) %>% 
  count(degree, name = "n_surg") %>% 
  rename(degree_record_nppes = degree) %>% 
  kable_df()
```

- Carrier Not GS, NPPES GS

NPPES specialty Taxonomy code have one to many relation with medicare specialty group.  Below are the surgeons who didn't link with Medicare data, but is defined as GS in NPPES, who have more than one medicare specialty (873/1260).

```{r QA_surg}
qa_surg_gs_npi_no_gs_carrier %>% 
  select(npi, medicare_specialty_code,medicare_provider_supplier_type_description) %>% 
  add_count(npi) %>% 
  filter(n>1) %>% 
  count(medicare_provider_supplier_type_description, name = "n surg", sort = T) %>% 
  kable_df()
```



- Milestone link with Medicare (5 Procedures)

```{r linked}
milestone_medicare = milestone_medicare%>% 
  mutate(linked_with_medicare = ifelse(is.na(id), "no", "yes"))

linked_surg = milestone_medicare %>% 
  distinct(npi.linked, carrier_nppes_gs, npi_nppes_gs, linked_with_medicare)

medicare_milestone_stat = linked_surg %>% 
  count(carrier_nppes_gs, npi_nppes_gs, linked_with_medicare, name = "n linked surgs") %>% 
  mutate(perc = scales::percent(`n linked surgs`/sum(`n linked surgs`))) %>%
  arrange(linked_with_medicare) 

medicare_milestone_stat %>% 
  select(- linked_with_medicare) %>%
  kable_df() %>% 
  group_rows("No Medicare Case", 1,4) %>% 
  group_rows("Linked with Medicare Case", 5,8) 

n_linked = medicare_milestone_stat %>%
  filter(linked_with_medicare == "yes") %>% select(`n linked surgs`) %>% sum()

n_no_linked = medicare_milestone_stat %>%
  filter(linked_with_medicare == "no") %>% select(`n linked surgs`) %>% sum()
  
```

the number of linked surgeons is `r n_linked`; the number of not linked surgeons is `r n_no_linked`

837 surgeons were both defined as GS in NPPES and Carrier; that is `r scales::percent(round((837+107)/(837+107+12+92), 2))`of all linked GS surgeons based on Carrier file definition.




