---
title: "Milestone Evals"
author: "Xilin Chen"
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  dev = 'png',
  fig.align = 'center',
  cache = F
  # out.width = '100%',
  # fig.asp = .5,
)    

library(tidyverse)
library(kableExtra)
library(lubridate)
library(tidyext)


kable_df <- function(..., digits=2) {
  kable(...,digits = digits) %>% 
    kable_styling(full_width = F, latex_options = "hold_position")
}
```

This document explores the milestone ratings for the last year evaluation. in the end, we will explore "Which Milestone subcompetencies are rated disproportionately lowest at
time of graduation?"

```{r load_data}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_final_year.rdata")
load("data/person_in_medicare_and_milestone.rdata")

milestone_in_medicare = milestone_final_year %>% 
  mutate(IntResponseValue = ifelse(IntResponseValue == 0, NA, IntResponseValue)) %>% 
  filter(grepl("Year-End",eval_peroid),
         PersonID %in% person_values$PersonID)
```


# Descriptive of Milestone

Evaluations are from 2015 to 2018, Mid-year and Year-end evals within each year. The number of graduates in milestone evals and also in Medicare are `r n_distinct(milestone_in_medicare$PersonID)`

```{r evals}
milestone_in_medicare %>% 
  mutate(grad_year = as.numeric(AcademicYear) +1) %>% 
  distinct(grad_year, PersonID) %>% 
  cat_by(grad_year) %>% 
  rename(n_suregons = N) %>% 
  kable_df(caption = "surgeons included in analysis")
```

5 surgeons who graduted after 2016 had medicare billings.


# Eval distribution by categories

```{r low_eval_distribultion}
milestone_in_medicare %>% 
  filter(!is.na(IntResponseValue)) %>% 
  count(IntResponseValue, ReportCategory) %>% 
  ggplot(aes(x = IntResponseValue, y = ReportCategory)) +
  geom_point(aes(size = n), color = "gray50")


milestone_in_medicare %>% 
  filter(QuestionKey %in% c("comp1_PC_Q3", "comp2_MK_Q2", "comp6_ICS_Q3")) %>% 
  ggplot(aes(x = IntResponseValue)) +
  stat_count(color = "gray50") +
  ggtitle("Operative Rating (PC3, MK2, ICS3)") +
  theme_classic()

milestone_in_medicare %>% 
  filter(ReportCategory == "Professionalism") %>% 
  ggplot(aes(x = IntResponseValue)) +
  stat_count(color = "gray50") +
  ggtitle("Professionalism (Prof1, Prof 2, Prof3)") +
  theme_classic()

```

# How many residents have <7 evals

```{r low_eval_ppl}
milestone_in_medicare %>% 
  filter(IntResponseValue<7) %>% 
  summarise(n_trainees_less_7 = length(unique(PersonID)),
            n_tot_trainees = length(unique(milestone_in_medicare$PersonID))) %>% 
  kable_df()
```


## percentage of having <7 rating in each category

Which Milestone subcompetencies are rated disproportionately lowest at
time of graduation?

```{r perc_less_7}
milestone_in_medicare %>% 
  mutate(low_rating = as.numeric(IntResponseValue)<7) %>% 
  group_by(ReportCategory) %>% 
  mutate(perc_low_rating = scales::percent(mean(low_rating, na.rm = TRUE), accuracy = 0.01),
         n_questions = n()) %>% 
  distinct(ReportCategory, perc_low_rating, n_questions) %>% 
  arrange(perc_low_rating) %>% 
  kable_df(caption  = "percentage of lower ratings (<7) in each question category")
```



