---
title: "Descriptive Stats for Milestone Medicare 2015-2017"
subtitle: "Max `r params$n_month` months after graduation"
author: "Xilin Chen"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
params:
  n_month: 24
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  fig.align = 'center',
  cache = F
)

library(tidyverse)
library(DT)
library(tidyext)
library(kableExtra)
library(arsenal)
library(glmmTMB)
library(mixedup)
library(ggeffects)
library(gtsummary)


kable_df <- function(..., digits=2) {
  kable(...,digits = digits, booktabs = T) %>% 
    kable_styling(full_width = F,
                  latex_options = c("striped", "hold_position"))
    # kable_styling(full_width = F)
}

source("~/Documents/Repo/Milestone_Medicare_Outcomes/code/functions/sum_table.R")

```


This document uses the end-year milestone evaluations at the last year of residency from ACGME. Milestone rating for each resident is the mean of all 16 questions. The cohort is linked medicare with milestone evals.


```{r load_data}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_ratings.rdata")

# keep valid rating score
milestone_medicare_pc = milestone_medicare_ratings %>% 
  filter(!is.na(IntResponseValue_mean),
         month <= params$n_month)

```

### 1. Cohort Data Description for Partial Colectomy

```{r data_desc}
milestone_medicare_pc = milestone_medicare_pc %>% 
  mutate(flg_cmp_po_any_not_poa = as.numeric(flg_cmp_po_any_not_poa),
         flg_cmp_po_severe_not_poa = as.numeric(flg_cmp_po_severe_not_poa)) %>% 
  mutate(
    open_colectomy = cpt_cd %in% c(44140:44147, 44160),
    lap_colectomy  = cpt_cd %in% 44204:44208,
    colectomy_type = factor(ifelse(
      cpt_cd %in% c(44140:44147, 44160), 'open', 'lap'
    ))
  ) 


milestone_medicare_pc %>% 
  summarise(n_case = n(),
            n_surgeon = length(unique(id_physician_npi)),
            n_hosp = length(unique(facility_prvnumgrp)),
            n_patient = length(unique(member_id)),
            POA_severe_complication_rate = sum(flg_cmp_po_severe_not_poa)/n_case,
            severe_complication_rate = sum(flg_cmp_po_severe)/n_case,
            POA_any_complication_rate = sum(flg_cmp_po_any_not_poa)/n_case,
            any_complication_rate = sum(flg_cmp_po_any)/n_case,
            death_rate = sum(flg_death_30d)/n_case,
            readmit_rate = sum(flg_readmit_30d)/n_case,
            reop_rate = sum(flg_util_reop)/n_case) %>% 
  mutate_at(vars(contains("rate")), scales::percent_format()) %>% 
  t() %>% 
  kable_df(caption = "Medicare Outcomes Description for PC")
```

details about each variables above:

- n_cases: number of medicare cases
- n_surgeons: number of surgeons
- n_hosp: number of hospitals
- n_patient: number of patients
- POA_severe_complication_rate: this was used for model outcomes instead of severe_complication; it's defined as severe complication within 30 days after the operation; the length of stay is >= 75% of this procedure in medicare and had any complication. 
- death_rate: death within 30days after the procedure
- readmit: readmission within 30days


#### 1.1 months after graduation 

number of cases and surgeons in medicare at each month after graduation

```{r month_case}
milestone_medicare_pc %>% 
  group_by(month) %>%
  mutate(n_cases = n(),
         n_surgeons = n_distinct(id_physician_npi)) %>% 
  distinct(month, n_cases, n_surgeons) %>% 
  arrange(month) %>% 
  rename(month_after_grad = month) %>% 
  DT::datatable(rownames = F)
```

Note: trainees who graduated in 2017 only had 6 months medicare cases.


#### 1.2 By Graduation Year


```{r trainees_by_year}
milestone_medicare_pc %>% 
  group_by(grad_year) %>% 
  summarise("numer of cases" = n(),
            "number of surgeons" = length(unique(id_physician_npi)),
            "cases per surgeon" = `numer of cases`/`number of surgeons`) %>%
    kable_df(caption = paste0("number of medicare cases within ", params$n_month, "months of graduation"))



surg_case_year = left_join(
  milestone_medicare_pc %>%
    group_by(facility_clm_yr) %>%
    distinct(id_physician_npi, grad_year) %>%
    count(grad_year, name = "number of surgeons")  %>%
    mutate(facility_clm_yr = facility_clm_yr + 2007) ,
  milestone_medicare_pc %>%
    group_by(facility_clm_yr) %>%
    count(grad_year, name = "number of cases")  %>%
    mutate(facility_clm_yr = facility_clm_yr + 2007)
) %>% 
  ungroup()

surg_case_year %>% 
  DT::datatable(caption = "number of surg and cases by graduation year and medicare year", rownames = F)

```

#### 1.3 Case Specs in the cohort

```{r pt_specs}
milestone_medicare_pc %>% 
  select(flg_male, age_at_admit, race_white,AHRQ_score, flg_admit_emerg,
         hosp_beds_2grp, colectomy_type) %>% 
  tbl_summary(missing = "no")




```

Note: 

- hosp_beds_2grp :(0.<349, 1: >=350)
- lap vs. open: 
  - open =  cpt_cd %in% c(44140:44147, 44160),
  - lap = cpt_cd %in% 44204:44208
- [AHQR score](https://www.ingentaconnect.com/content/wk/mcar/2017/00000055/00000007/art00010) reference paper


### 2. Milestone Ratings vs Descriptive stats

Milestone ratings range from 1 to 9; 0 rating is categorized as "not yet assessable" as NA in data.

Binary ratings for milestones are defined as:

- 0 : mean milestone ratings <8
- 1 : mean milestone ratings >=8

```{r rating}
person_rating = milestone_medicare_pc %>%
  distinct(
    id_physician_npi,
    IntResponseValue_mean,
    never_less_8_rating,
    mean_ge_8,
    
    prof_rating_mean,
    prof_rating_ge8,
    
    operative_rating_mean,
    operative_rating_ge8,
    
    leadership_rating_mean,
    leadership_rating_ge8
  )
```


```{r conditional_prob, eval = F}
# Descriptive Conditional Probabilities

# not show in report
dt = milestone_medicare_pc %>%
  transmute(overall_mean = round(IntResponseValue_mean),
            mean_ge_8,
            flg_death_30d) %>% 
  mutate(overall_mean = as.factor(overall_mean))

dt %>%
  count(overall_mean, flg_death_30d) %>%
  pivot_wider(names_from = flg_death_30d,
              values_from = n) %>%
  rename(n_death = `1`,
         n_alive = `0`) %>%
  mutate(
    n_all = n_alive + n_death,
    `P(death|rating)` = n_death / n_all,
    prob_rating = n_all / sum(n_all),
    `P(death and certain rating)` = `P(death|rating)` * prob_rating
  ) %>%
  select(-prob_rating, -n_all) %>%
  mutate_at(vars(contains("p(")), scales::percent_format()) %>% 
  kable_df()

dt %>%
  count(mean_ge_8, flg_death_30d) %>%
  pivot_wider(names_from = flg_death_30d,
              values_from = n) %>%
  rename(n_death = `1`,
         n_alive = `0`) %>%
  mutate(
    n_all = n_alive + n_death,
    `P(death|rating)` = n_death / n_all,
    prob_rating = n_all / sum(n_all),
    `P(death and certain rating)` = `P(death|rating)` * prob_rating
  ) %>%
  select(-prob_rating, -n_all) %>%
  mutate_at(vars(contains("p(")), scales::percent_format()) %>% 
  kable_df()


```


#### 2.1 Overall mean of 16 milestone ratings

```{r mean_overall}
# mean overall------
# debugonce(sum_table)
sum_table(rating_var = IntResponseValue_mean, 
          name = "overall_mean")
```


**Overall mean milestone ratings greater or equal to 8**

Note: not matched with the numbers above because of rounding.

```{r mean_lt_8}
# overall mean less than 8 -----
sum_table(rating_var = mean_ge_8, 
          name = "overall_mean_gt_8")
```


#### 2.2 professional ratings mean (comp5_PR_Q1, comp5_PR_Q2, comp5_PR_Q3)

```{r prof_rating_mean}
# prof_rating_mean -----
sum_table(rating_var = prof_rating_mean, 
          name = "prof_rating_mean")
```

**Mean of professional ratings are greater or equal to 8**

```{r prof_rating_mean2}
sum_table(rating_var = prof_rating_ge8, 
          name = "prof_rating_ge8")

```

#### leadership ratings mean (comp5_PR_Q1, comp6_ICS_Q1, comp6_ICS_Q2, comp3_SBP_Q")

```{r leadership_rating_mean}
# leadership_rating_mean----
sum_table(rating_var = leadership_rating_mean, 
          name = "leadership_rating_mean")
```

**Mean of leadership ratings are greater or equal to 8**

```{r leadership_rating_mean2}
sum_table(rating_var = leadership_rating_ge8, 
          name = "leadership_rating_ge8")
```

#### Operative ratings mean (PC3, MK2, ICS3)

```{r operative_rating_mean}
# operative_rating_mean---
sum_table(rating_var = operative_rating_mean, 
          name = "operative_rating_mean")
```

**Mean of operative ratings are greater or equal to 8** 

```{r operative_rating_mean2}
sum_table(rating_var = operative_rating_ge8, 
          name = "operative_rating_ge8")

```



<!-- ####  Death Descriptive -->

<!-- ```{r death} -->
<!-- death_case = milestone_medicare_pc %>% -->
<!--   filter(flg_death_30d == 1) %>% -->
<!--   transmute( -->
<!--     overall_mean = round(IntResponseValue_mean), -->
<!--     flg_death_30d, -->
<!--     # covers -->
<!--     flg_male, -->
<!--     age_at_admit, -->
<!--     race_white, -->
<!--     race_hisp_other, -->
<!--     flg_admit_emerg, -->
<!--     AHRQ_score, -->
<!--     ses_2grp, -->
<!--     # 'cpt_cd', -->
<!--     facility_clm_yr, -->
<!--     flg_multi_surgeon, -->
<!--     flg_assistant_surgeon, -->
<!--     hosp_beds_2grp, -->
<!--     # 'flg_hosp_ICU_hosp', -->
<!--     val_hosp_mcday2inptday_ratio, -->
<!--     val_hosp_rn2bed_ratio -->
<!--   ) -->
<!-- ``` -->

<!-- Based on the model results, age(negative), admit emergent (negative) status and multiple surgeons performance (positive) are 3 variables that had statistically significance on death within 30 days. Below are the descriptive stats for each overall milestone score. -->

<!-- ```{r death_cov} -->
<!-- case_by_mean_milestone = milestone_medicare_pc %>%  -->
<!--   mutate(overall_mean = round(IntResponseValue_mean)) %>%  -->
<!--   group_by(overall_mean) %>%  -->
<!--   summarise(n_case = n())  -->

<!-- death_case %>% -->
<!--   group_by(overall_mean) %>% -->
<!--   summarise(n_cases_death = n(), -->
<!--             emergent_admit_rate = mean(flg_admit_emerg, na.rm = T), -->
<!--             emergent_admit_rate = scales::percent(emergent_admit_rate), -->
<!--             age = mean(age_at_admit), -->
<!--             multi_surg = mean(flg_multi_surgeon), -->
<!--             multi_surg = scales::percent(multi_surg)) %>%  -->
<!--   left_join(case_by_mean_milestone) %>%  -->
<!--   select(overall_mean, n_case, n_cases_death, everything()) %>%  -->
<!--   kable_df() -->
<!-- ``` -->

<!-- In order to understand the milestone rating vs. death relationship, without considering other covariates. Below are the univariate analysis between death within 30 days and mean of milestone rating for 30 months practice -->

<!-- ```{r uni_model_death} -->
<!-- load("~/Documents/Repo/Milestone_Medicare_Outcomes/data/uni_death_model_no_limit_model.rdata") -->

<!-- uni_death_model_no_limit %>%  -->
<!--   mutate(OR = exp(estimate)) %>%  -->
<!--   select(term, OR, everything()) %>%  -->
<!--   kable_df() -->
<!-- ``` -->

<!-- Without controlling for covariate, higher overall milestone ratings had lower patient mortality rate. -->

