---
title: "Descriptive Stats for Milestone Medicare 2007-2017"
author: "Xilin Chen"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  fig.align = 'center',
  cache = F
)

library(tidyverse)
library(DT)
library(tidyext)
library(kableExtra)
library(arsenal)
library(glmmTMB)
library(mixedup)
library(ggeffects)


kable_df <- function(..., digits=2) {
  kable(...,digits = digits, booktabs = T) %>% 
    kable_styling(full_width = F,
                  latex_options = c("striped", "hold_position"))
    # kable_styling(full_width = F)
}

sum_table <- function(name = "overall_mean",
                      rating_var = IntResponseValue_mean) {
  rating_var = enquo(rating_var)

  milestone_medicare_pc %>%
    mutate(!!name := round(!!rating_var)) %>%
    group_by(!!!syms(name)) %>%
    mutate(
      n_surgeons = length(unique(id_physician_npi)),
      n_cases = n(),
      n_severe_cmp_poa = sum(flg_cmp_po_severe_not_poa),
      rate_severe_cmp_poa = n_severe_cmp_poa / n_cases,
      n_death = sum(flg_death_30d),
      rate_death = n_death / n_cases,
      n_reop = sum(flg_util_reop),
      rate_reop = n_reop / n_cases,
      n_readmit = sum(flg_readmit_30d),
      rate_readmit = n_readmit / n_cases
    ) %>%
    ungroup() %>%
    distinct(
      !!!syms(name),
      n_surgeons,
      n_cases,
      n_severe_cmp_poa,
      rate_severe_cmp_poa,
      n_death,
      rate_death,
      n_reop,
      rate_reop,
      rate_reop,
      n_readmit,
      rate_readmit
    ) %>%
    arrange(!!!syms(name)) %>%
    datatable(rownames = F, options = list(scrollX = T)) %>%
    formatPercentage(c(
      'rate_severe_cmp_poa',
      'rate_death',
      'rate_reop',
      'rate_readmit'
    ),
    2)
}

```


This document uses the end-year milestone evaluations at the last year of residency from ACGME. Milestone rating for each resident is the mean of all 16 questions. The data is linked medicare with milestoner evals.

### Number of cases by procedure

```{r load_data}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_ratings.rdata")

milestone_medicare_ratings %>% 
  count(e_proc_grp_lbl, sort = T, name = "n_cases") %>% 
  DT::datatable()

```


### Whole Cohort Data Description for Partial Colectomy

```{r data_desc}
milestone_medicare_pc = milestone_medicare_ratings %>% 
  filter(proc_Partial_Colectomy==1) %>% 
  mutate(flg_cmp_po_any_not_poa = as.numeric(flg_cmp_po_any_not_poa),
         flg_cmp_po_severe_not_poa = as.numeric(flg_cmp_po_severe_not_poa))


milestone_medicare_pc %>% 
  summarise(n_case = n(),
            n_surgeon = length(unique(id_physician_npi)),
            n_hosp = length(unique(facility_prvnumgrp)),
            POA_severe_complication_rate = sum(flg_cmp_po_severe_not_poa)/n_case,
            severe_complication_rate = sum(flg_cmp_po_severe)/n_case,
            POA_any_complication_rate = sum(flg_cmp_po_any_not_poa)/n_case,
            any_complication_rate = sum(flg_cmp_po_any)/n_case,
            death_rate = sum(flg_death_30d)/n_case,
            readmit = sum(flg_readmit_30d)/n_case,
            reop = sum(flg_util_reop)/n_case) %>% 
  t() %>% 
  kable_df(caption = "Medicare Outcomes Description for PC")
```

### Trainees by Year

```{r trainees_by_year}
milestone_medicare_pc %>% 
  distinct(id_physician_npi, grad_year) %>% 
  count(grad_year, name = "number of surgeons") %>% 
  kable_df(caption = "number of sugeons by graduation year in medicare PC")


milestone_medicare_pc %>% 
  count(grad_year, name = "number of cases") %>% 
  kable_df(caption = "number of cases by graduation year in medicare PC")

surg_case_year = left_join(
  milestone_medicare_pc %>%
    group_by(facility_clm_yr) %>%
    distinct(id_physician_npi, grad_year) %>%
    count(grad_year, name = "number of surgeons")  %>%
    mutate(facility_clm_yr = facility_clm_yr + 2007) ,
  milestone_medicare_pc %>%
    group_by(facility_clm_yr) %>%
    count(grad_year, name = "number of cases")  %>%
    mutate(facility_clm_yr = facility_clm_yr + 2007)
) %>% 
  mutate(`cases per surg` = `number of cases`/`number of surgeons`,
         `cases per surg` = round(`cases per surg`, 2) )  %>%
  ungroup()

surg_case_year %>% 
  DT::datatable(caption = "number of surg and cases by graduation year and medicare year")

```



### Milestone Ratings vs Descriptive Outcomes for Patial Colectomy

```{r rating}
person_rating = milestone_medicare_pc %>%
  distinct(
    id_physician_npi,
    IntResponseValue_mean,
    never_less_8_rating,
    mean_ge_8,
    
    prof_rating_mean,
    prof_rating_ge8,
    
    operative_rating_mean,
    operative_rating_ge8,
    
    leadership_rating_mean,
    leadership_rating_ge8
  )
```

#### Overall mean of 16 milestone ratings

```{r mean_overall}
# mean overall------
# debugonce(sum_table)
sum_table(rating_var = IntResponseValue_mean, 
          name = "overall_mean")
```

#### overall mean milestone ratings less than 8 

Note: not matched with the numbers above because of rounding.

```{r mean_lt_8}
# overall mean less than 8 -----
sum_table(rating_var = mean_ge_8, 
          name = "overall_mean_gt_8")
```

#### Any Milestone ratings less than 8

```{r ever_lt_8}
# ever_less_8_rating-----
sum_table(rating_var = never_less_8_rating, 
          name = "never_have_lt8_rating")
```

#### professional ratings mean (comp5_PR_Q1, comp5_PR_Q2, comp5_PR_Q3)

```{r prof_rating_mean}
# prof_rating_mean -----
sum_table(rating_var = prof_rating_mean, 
          name = "prof_rating_mean")

sum_table(rating_var = prof_rating_ge8, 
          name = "prof_rating_ge_8")

```

#### leadership ratings mean (comp5_PR_Q1, comp6_ICS_Q1, comp6_ICS_Q2, comp3_SBP_Q")

```{r leadership_rating_mean}
# leadership_rating_mean----
sum_table(rating_var = leadership_rating_mean, 
          name = "leadership_rating_mean")

sum_table(rating_var = leadership_rating_ge8, 
          name = "leadership_rating_ge8")
```

#### Operative ratings mean (PC3, MK2, ICS3)

```{r operative_rating_mean}
# operative_rating_mean---
sum_table(rating_var = operative_rating_mean, 
          name = "operative_rating_mean")

sum_table(rating_var = operative_rating_ge8, 
          name = "operative_rating_ge8")

```



