---
title: "Milestones and Medicare Outcome Descriptives"
date: "`r Sys.Date()`"
output: 
  pdf_document:
        toc: yes
        toc_depth: 5
---

```{r setup, include=FALSE}
# this report was used for the purpose of communication with external collaborators like ACGME
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  fig.align = 'center',
  cache = F
)

library(tidyverse)
library(knitr)
library(gtsummary)

source("code/functions/sum_tbl_by_rating.R")

```

Milestones vs Medicare outcomes cohort details

-	Medicare cases: inpatient from 2015-2017
-	Milestone graduates: 2015-2017
-	Procedure: Partial Colectomy
-	Practice months after graduation: 24 months


```{r load_data, cache=TRUE}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_pc_primary.rdata")
# model
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/model/models_month24_pc.rdata")


# keep valid rating score
milestone_medicare_pc = milestone_medicare_pc_primary %>% 
  mutate(hosp_beds = case_when(hosp_beds_2grp == 0 ~ "<350",
                               hosp_beds_2grp == 1 ~ ">=350")) %>% 
  filter(!is.na(IntResponseValue_mean),
         month <= 24)
```

## 1. Cohort Description

**Overall Cohort**
```{r cohort_desc}
milestone_medicare_pc = milestone_medicare_pc %>% 
  mutate(flg_cmp_po_any_not_poa = as.numeric(flg_cmp_po_any_not_poa),
         flg_cmp_po_severe_not_poa = as.numeric(flg_cmp_po_severe_not_poa)) %>% 
  mutate(
    open_colectomy = cpt_cd %in% c(44140:44147, 44160),
    lap_colectomy  = cpt_cd %in% 44204:44208,
    colectomy_type = factor(ifelse(
      cpt_cd %in% c(44140:44147, 44160), 'open', 'lap'
    ))
  ) 

# outcomes desc
summary_tbl = milestone_medicare_pc %>% 
  summarise(n_case = n(),
            n_surgeon = length(unique(id_physician_npi)),
            n_hosp = length(unique(facility_prvnumgrp)),
            n_patient = length(unique(member_id)),
            POA_severe_complication_rate = sum(flg_cmp_po_severe_not_poa)/n_case,
            # severe_complication_rate = sum(flg_cmp_po_severe)/n_case,
            POA_any_complication_rate = sum(flg_cmp_po_any_not_poa)/n_case,
            # any_complication_rate = sum(flg_cmp_po_any)/n_case,
            death_rate = sum(flg_death_30d)/n_case,
            readmit_rate = sum(flg_readmit_30d)/n_case,
            reop_rate = sum(flg_util_reop)/n_case) %>% 
  mutate_at(vars(contains("rate")), scales::percent_format()) %>% 
  t() 

summary_tbl %>% 
  kable(align = 'c')


```

**Case level characteristics**

```{r case_desc}
# case characters
milestone_medicare_pc %>% 
  select(flg_male, age_at_admit, race_white,AHRQ_score, flg_admit_emerg,
         had_assist_surg, colectomy_type,
         hosp_beds,  val_hosp_mcday2inptday_ratio,
      val_hosp_rn2bed_ratio) %>% 
  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})[{p25}, {p75}]"),
              missing = "no")
```
* val_hosp_mcday2inptday_ratio: Total facility medicaid days/total facility inpatient days ratio
* val_hosp_rn2bed_ratio: Registered nurse to  bed ratios
* for countious variables, the stats are *mean (sd)[p25, p75]*

## 2. Milestone ratings

### 2.1 Overall mean

#### Descriptive table

```{r overall_mean}
sum_tbl_by_rating(data = milestone_medicare_pc,
                  rating_var = mean_ge_8) 
```



### 2.2 Professional ratings 

#### Descriptive table

```{r prof}
sum_tbl_by_rating(data = milestone_medicare_pc,
                  rating_var = prof_rating_ge8)
```


### 2.3 Operative ratings

#### Descriptive table

```{r operative_desc}
sum_tbl_by_rating(data = milestone_medicare_pc,
                  rating_var = operative_rating_ge8)
```


### 2.4 Leadership ratings

#### Descriptive table

```{r lead_desc}
sum_tbl_by_rating(data = milestone_medicare_pc,
                  rating_var = leadership_rating_ge8)
```

### 2.5 Assistant surgeon cases and hospital size across ratings

#### Descriptive table

Summary table to look across 4 different milestone ratings by if *had_assist_surgeon* and *hospital bed size*.

```{r}
# maybe because of using PDF output, if using map, the output is html code instead of tables. So I repeated code.

sum_tbl_by_rating_assist(data = milestone_medicare_pc,
                  rating_var = "mean_ge_8") %>% 
  modify_header(label ~ "**overall_mean**")

sum_tbl_by_rating_assist(data = milestone_medicare_pc,
                  rating_var = "prof_rating_ge8") %>% 
  modify_header(label ~ "**Professional**")

sum_tbl_by_rating_assist(data = milestone_medicare_pc,
                  rating_var = "operative_rating_ge8") %>% 
  modify_header(label ~ "**Operative**")

sum_tbl_by_rating_assist(data = milestone_medicare_pc,
                  rating_var = "leadership_rating_ge8") %>% 
  modify_header(label ~ "**Leadership**")


```




