---
title: "`r params$outcome_name` Model Summary Report"
subtitle: "`r params$n_month` months max"
author: "Xilin Chen"
date: "`r Sys.Date()`"
always_allow_html: true
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
params:
  data: results
  outcome_name: outcome_name
  n_month: 12
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  fig.align = 'center',
  cache = F
)

library(tidyverse)
library(tidyext)
library(kableExtra)
library(arsenal)
library(glmmTMB)
library(mixedup)
library(ggeffects)


source("/Users/xilinchen/Documents/Repo/Milestone_Medicare_Outcomes/code/functions/fe.r")
source("/Users/xilinchen/Documents/Repo/Milestone_Medicare_Outcomes/code/functions/predictor_visual_from_model.R")

```


```{r load_data}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_ratings.rdata")
# load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/model/pc/rating_model.rdata")

# milestone data
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_final_year.rdata")

results = params$data



milestone_medicare_pc = milestone_medicare_ratings %>%
  filter(proc_Partial_Colectomy == 1) %>%
  mutate(
    flg_cmp_po_any_not_poa = as.numeric(flg_cmp_po_any_not_poa),
    flg_cmp_po_severe_not_poa = as.numeric(flg_cmp_po_severe_not_poa)
  )
```

# Description

This document uses the end-year milestone evaluations at the last year of residency from ACGME. Milestone rating for each resident is the mean of all questions. We only used Partial Colectomy procedure.

## Milestone question keys and descriptions

```{r milestone eval}
milestone_final_year %>% 
  distinct(ReportCategory, QuestionKey, QuestionText) %>% 
  filter(!is.na(ReportCategory)) %>% 
  DT::datatable()
```

## Table1 for model variables

```{r table1, results="asis"}
milestone_medicare_pc = milestone_medicare_pc %>% 
  filter(month <= params$n_month) %>% 
  mutate(
    # patient
    ses_2grp = factor(ses_2grp, labels = c('bot 2 quint', 'top 3 quint')),
    flg_admit_emerg = factor(flg_admit_emerg, labels = c('Not', 'Emergency')),
    flg_male = factor(flg_male, labels = c('Female', 'Male')),
    # case
    open_colectomy = cpt_cd %in% c(44140:44147, 44160),
    lap_colectomy  = cpt_cd %in% 44204:44208,
    colectomy_type = factor(ifelse(cpt_cd %in% c(44140:44147, 44160), 'open', 'lap')),
    # hosp
    facility_clm_yr = facility_clm_yr + 2007,
    hosp_beds_2grp = factor(hosp_beds_2grp, labels = c('<350', '>=350')),
  )


table_one <- tableby( ~ flg_male + age_at_admit + factor(e_race_wbho_lable) + AHRQ_score + ses_2grp + colectomy_type + factor(facility_clm_yr) + factor(flg_multi_surgeon) + factor(flg_assistant_surgeon)  + hosp_beds_2grp + val_hosp_mcday2inptday_ratio + val_hosp_rn2bed_ratio, data = milestone_medicare_pc)

mylabels <- list(val_hosp_mcday2inptday_ratio = "medicaid/inpatient days ratio", val_hosp_rn2bed_ratio = "Registered nurse to bed ratios")

summary(table_one, labelTranslations = mylabels)
```


## Outcomes: `r params$outcome_name`

### 1.1 Overall Mean

```{r overall_mean}
overall_mean = results$Par_all_mean

fe(overall_mean)

extract_vc(overall_mean, ci_level = 0) %>% 
    kable_df() 


# # predicted probability for surgeons
# model_vis(results$Par_severe_cmp_all_mean)


```


### 1.2 Overall mean greater or equal to 8

mean less than 8 is the reference group

```{r mean_lt8}
mean_ge_8 = results$Par_mean_ge_8

fe(mean_ge_8)

extract_vc(mean_ge_8, ci_level = 0) %>%
    kable_df()

```



### 1.3 Any rating greater or equal to 8

```{r ever_lt8}
never_lt_8 = results$Par_never_less_8

fe(never_lt_8)

extract_vc(never_lt_8, ci_level = 0) %>%
    kable_df()

```


### 2.1 Professional Mean

```{r prof_mean}
prof_mean = results$Par_prof

fe(prof_mean)

extract_vc(prof_mean, ci_level = 0) %>%
    kable_df()

```

### 2.2 Professional greater or equal to 8

```{r prof_8}
prof_ge_8 = results$Par_prof_ge8

fe(prof_ge_8)

extract_vc(prof_ge_8, ci_level = 0) %>%
    kable_df()

```


### 3.1 Operative ratings

```{r opera_mean}
operative_mean = results$Par_operative

fe(operative_mean)

extract_vc(operative_mean, ci_level = 0) %>%
    kable_df()

```


### 3.2 Operative ratings greater or equal to 8

```{r opera_8}
operative_ge8 = results$Par_operative_ge8

fe(operative_ge8)

extract_vc(operative_ge8, ci_level = 0) %>%
    kable_df()
```


### 4.1 Leadership ratings

```{r lead_mean}
lead_mean = results$Par_leadership

fe(lead_mean)

extract_vc(lead_mean, ci_level = 0) %>%
    kable_df()

```


### 4.2 Leadership ratings less than 8

```{r lead_lt8}
lead_ge8 = results$Par_leadership_ge8

fe(lead_ge8)

extract_vc(lead_ge8, ci_level = 0) %>%
    kable_df()
```



