---
title: "Model Summary"
author: "Xilin Chen"
date: "2/26/2020"
always_allow_html: true
output:
  html_document:
    toc: true
    toc_depth: 1
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,                                     # code
  message = F,
  warning = F,
  error = F,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),          # viz
  dev = 'png',
  fig.align = 'center',
  cache = F
  # out.width = '100%',
  # fig.asp = .5,
)

library(tidyverse)
library(tidyext)
library(kableExtra)
library(arsenal)
library(glmmTMB)
library(mixedup)
library(ggeffects)


kable_df <- function(..., digits=2) {
  kable(...,digits = digits, booktabs = T) %>% 
    kable_styling(full_width = F,
                  latex_options = c("striped", "hold_position"))
    # kable_styling(full_width = F)
}



source("/Users/xilinchen/Documents/Repo/Milestone_Medicare_Outcomes/code/functions/fe.r")
source("/Users/xilinchen/Documents/Repo/Milestone_Medicare_Outcomes/code/functions/predictor_visual_from_model.R")

```


```{r load_data}
load("/Volumes/George_Surgeon_Projects/Milestone_vs_Outcomes/milestone_medicare_pc.rdata")
```

# Description

This document uses the end-year milestone evaluations at the last year of residency from ACGME. Milestone rating for each resident is the mean of all questions.

# Whole Data Description

```{r data_desc}
milestone_medicare_pc %>% 
  summarise(n_case = n(),
            n_surgeon = length(unique(id_physician_npi)),
            n_hosp = length(unique(facility_prvnumgrp)),
            POA_severe_complication_rate = sum(flg_cmp_po_severe_poa)/n_case,
            severe_complication_rate = sum(flg_cmp_po_severe)/n_case,
            POA_any_complication_rate = sum(flg_cmp_po_any_poa)/n_case,
            any_complication_rate = sum(flg_cmp_po_any)/n_case,
            death_rate = sum(flg_death_30d)/n_case,
            readmit = sum(flg_readmit_30d)/n_case,
            reop = sum(flg_util_reop)/n_case) %>% 
  t() %>% 
  kable_df(caption = "Medicare Outcomes Description")
```


## Table1 for model variables

```{r table1, results="asis"}
milestone_medicare_pc = milestone_medicare_pc %>% 
  mutate(
    # patient
    ses_2grp = factor(ses_2grp, labels = c('bot 2 quint', 'top 3 quint')),
    flg_admit_emerg = factor(flg_admit_emerg, labels = c('Not', 'Emergency')),
    flg_male = factor(flg_male, labels = c('Female', 'Male')),
    # case
    open_colectomy = cpt_cd %in% c(44140:44147, 44160),
    lap_colectomy  = cpt_cd %in% 44204:44208,
    colectomy_type = factor(ifelse(cpt_cd %in% c(44140:44147, 44160), 'open', 'lap')),
    # hosp
    facility_clm_yr = facility_clm_yr + 2007,
    hosp_beds_2grp = factor(hosp_beds_2grp, labels = c('<350', '>=350')),
  )


table_one <- tableby( ~ IntResponseValue_mean + prof_rating_mean + operative_rating_mean + ever_less_7_rating + flg_male + age_at_admit + factor(e_race_wbho_lable) + AHRQ_score + ses_2grp + colectomy_type + factor(facility_clm_yr) + factor(flg_multi_surgeon) + factor(flg_assistant_surgeon)  + hosp_beds_2grp + val_hosp_mcday2inptday_ratio + val_hosp_rn2bed_ratio, data = milestone_medicare_pc)

mylabels <- list(val_hosp_mcday2inptday_ratio = "medicaid/inpatient days ratio", val_hosp_rn2bed_ratio = "Registered nurse to bed ratios")

summary(table_one, labelTranslations = mylabels)
```


\newpage


```{r rating_desc}
# main predictor
predict_term = extract_fixed_effects(results$flg_cmp_po_severe_poa) %>% 
  slice(2) %>% 
  pull(term)


milestone_medicare_pc %>% 
  ggplot() +
  geom_bar(aes_string(x = predict_term)) +
  theme_classic() 

milestone_medicare_pc %>% 
  num_by(predict_term) %>% 
  kable_df()
```


\newpage


# Severe Complication (Excluded POA)

```{r severe_cmp}
model_severe_cmp = results$flg_cmp_po_severe_poa

fe(model_severe_cmp)

extract_vc(model_severe_cmp, ci_level = 0) %>% 
    kable_df() 


# predicted probability for surgeons
model_vis(results$flg_cmp_po_severe_poa)


```





\newpage

# Any Complication (Exclude POA)

```{r any_cmp}
model_any_cmp = results$flg_cmp_po_any_poa

fe(model_any_cmp)

extract_vc(model_any_cmp, ci_level = 0) %>%
    kable_df()

# predicted probability for surgeons
model_vis(results$flg_cmp_po_any_poa)

```

\newpage


# Readmit 30 days

```{r readmit}
flg_readmit_30d = results$flg_readmit_30d

fe(flg_readmit_30d)

extract_vc(flg_readmit_30d, ci_level = 0) %>%
    kable_df()

# predicted probability for surgeons
model_vis(results$flg_readmit_30d)
```


\newpage


# Death 30 days

```{r death}
flg_death_30d = results$flg_death_30d

fe(flg_death_30d)

extract_vc(flg_death_30d, ci_level = 0) %>%
    kable_df()

# predicted probability for surgeons
model_vis(results$flg_death_30d)

```


\newpage


# Reoperation

```{r reoperation}
flg_util_reop = results$flg_util_reop

fe(flg_util_reop)

extract_vc(flg_util_reop, ci_level = 0) %>%
    kable_df()

# predicted probability for surgeons
model_vis(results$flg_util_reop)

```


\newpage


# Any Complication Exclude Death

```{r complication}
flg_any_but_death = results$flg_any_but_death

fe(flg_any_but_death)

extract_vc(flg_any_but_death, ci_level = 0) %>%
    kable_df()

# predicted probability for surgeons
model_vis(results$flg_any_but_death)

```